EuPPollNet: A European database of plant-pollinator networks

### 2024-05-15 Manuscript/EuPPollNet_Ms.qmd
edits

Bees conducted the majority of the interactions at the metaweb level, but their relative relevance changed across habitats and bioclimatic regions. For instance, plant-pollinator communities in the Mediterranean were dominated by bees, while communities in Alpine or Boreal regions were especially fly species rich or fly-dominated. These patterns are consistent with our current understanding of bee diversity, which peaks in dry or temperate areas [@orr2021; @leclercq2023]; and with the fact that colder environments (i.e., altitude and latitude wise) harbor a larger fraction of fly pollinators compared to other taxa [@elberling1999; @lefebvre2018]. In addition, beetles were only species rich in the Mediterranean region.

Comment on
Coleoptera -sampling methodology-
Lepidoptera -Ollerton ref, global context-

Bee diversity peaked in the Mediterranean area as found in previous large scale comparisons [REF] and beetles were particularly relevant in this region

, while non-bee insects such as syrphids were particularly relevant in colder 
non-bee insect pollinators were particularly relevant

Hymenoptera and Diptera had a similar number of species, the majority of interactions were conducted by bees.

Bees conducted the majority of interactions within the database which is in agreement with previous large scale studies conducted in Europe [REF].

and for the majority of Angiosperm species worldwide [@ollerton2017]. The proportion of the major pollinator orders within the database

Despite Hymenoptera and Diptera species have a similar number of species within the database, bees conducted most of the interactions as found in previous large scale studies [@Lanuza2023].

Ollerton
Myself
Someone else?

Despite a similar number of Hymenoptera and Diptera species, most of the interactions were done by Hymenoptera species (i.e., mainly bees). Notably,

Ollerton
Contextualise European diversity of plant and pollinator species with global biodiveristy

Network metric paragraph?
This higher number of pollinator species compared to plants seems to be a common feature of phytocentric sampled plant-pollinator networks [@jordano2016].

@@

Paragraph

Habitat type and bioclimatic region

Minor things to say
-Presence of honey bees in context with previous studies
Maybe cite Proc B and myself?

Although Europe...

Geographic and taxonomic biases!
Supporting reference:
https://doi.org/10.1111/ecog.05926

@@

>>>>

Bees conducted the majority of the interactions at the metaweb level, but their relative relevance changed across habitats and bioclimatic regions. For instance, plant-pollinator communities in the Mediterranean were dominated by bees, while communities in Alpine or Boreal regions were especially fly species rich or fly-dominated. These patterns are consistent with our current understanding of bee diversity, which peaks in dry or temperate areas [@orr2021; @leclercq2023]; and with the fact that colder environments (i.e., altitude and latitude wise) harbor a larger fraction of fly pollinators compared to other taxa [@elberling1999; @lefebvre2018]. In addition, beetles were only species rich in the Mediterranean region. Although the networks from the database are visitation networks and do not capture pollinator efficiency [@ballantyne2015], the high proportion of beetles as floral visitors in the Mediterranean provides further support for their role as pollinators in this region [@herrera2019; @leon2022]. The number of butterfly species and interactions were relatively low compared to the other taxa. Although Europe contains a little number of butterfly species compared to other areas of the world [@ollerton2017], their relevance as pollinators is likely under-estimated within this database as sampling methodologies for other insects pollinators (e.g., bees or flies) generally require less sampling distance and cover less space. Honey bees did one third of the total recorded interactions per network, highlighting their high abundances in natural communities and possibly impacting negatively wild pollinators.

-Presence of honey bees in context with previous studies
Maybe cite Proc B and myself?

**Network paragraph**

This higher number of pollinator species compared to plants seems to be a common feature of phytocentric sampled plant-pollinator networks [@jordano2016].

@@

@@

**Conclusion paragraph**
Geographic and taxonomic biases!
Supporting reference:
https://doi.org/10.1111/ecog.05926
